The problem and promise of scale in multilayer networks

### 2019-09-27 paper/table1.Rmd
rm old pander

---
output: 
  # pdf_document
# classoption: landscape
  word_document:
    reference_docx: template.docx
  # github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "`r Sys.Date()`"
---

### Table 1
In Table 1, we define three types of multilayer networks that incorporate spatial variables. Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers represent the different types of relationships, individuals or contexts of the social system. Nodes represent individual entities in the network, connected by some association or relationship with edges. Interlayer edges connect layers to other layers or individuals across layers. Intralayer edges connect individuals to other individuals within a network layer.

@@

TODO: find pictures of ML nets to include

```{r, echo = FALSE, warning = FALSE}
# library(pander)
# panderOptions('table.alignment.default', function(df)
#     ifelse(sapply(df, is.numeric), 'right', 'left'))
# panderOptions('table.split.table', Inf)
# panderOptions('big.mark', ",")
# panderOptions('keep.trailing.zeros', TRUE)

library(data.table)
library(magrittr)
library(kableExtra)

>>>>

---
output: 
  # word_document:
  #   reference_docx: template.docx
  github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "`r Sys.Date()`"
bibliography: ../references/refs.bib

---

### Table 1
In Table 1, we describe three types of multilayer networks that incorporate spatial variables. Multilayer networks are composed of layers, nodes and edges. Layers represent different types of relationships

The edges are often abstracted because they no longer in the sense that they represent a specific spatial and temporal context, which

[@dale2017applying]

Layers represent the different types of relationships, individuals or contexts of the social system. Nodes represent individual entities in the network, connected by some association or relationship with edges. Interlayer edges connect layers to other layers or individuals across layers. Intralayer edges connect individuals to other individuals within a network layer.

Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)

Layers represent a type of edge (e.g.: grooming and association), entity (e.g.: male and female, or different species), or spatial context (e.g.: landcover type, patch).

@@

```{r, echo = FALSE, warning = FALSE}
library(data.table)
